Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-18 prop_iop.tex
prop_iop.tex \subsection{Restricting the Event Space} Starting...
prop_iop.tex Updating citations...

Since Gleason's theorem supports the idea of von Neumann to define
a state as a density matrix~\cite{Varadarajan2008}, a density matrix
might not be a adequate imprecise quantum state. Instead, a imprecise
quantum state might be more like an interactive system suggested by
Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
which would interact differently with different clients. Furthermore,
the validity the fundamental theorems of quantum mechanics followed
up by Gleason's theorem, such as Bell~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
might need to be reassessed based on our imprecise measurement. Our
research then might provide a new insight to the old debate among
Meyer, Mermin, and others about whether finite precision measurement
would nullify the Kochen-Specker theorem or not~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.

@@

>>>>

Since Gleason's theorem supports the idea of von Neumann to define
a state as a density matrix~\cite{Varadarajan2008}, a density matrix
might not be a adequate imprecise quantum state. Instead, a imprecise
quantum state might be more like an interactive system suggested by
Quantum Bayesianism or QBism~\cite{FuchsSchack2013,FuchsMerminSchack2014,VonBaeyer2016},
which would interact differently with different clients. Furthermore,
the validity the fundamental theorems of quantum mechanics followed
up by Gleason's theorem, such as Bell~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007},
might need to be reassessed based on our imprecise measurement. Our
research then might provide a new insight to the old debate among
Meyer, Mermin, and others about whether finite precision measurement
would nullify the Kochen-Specker theorem or not~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004}.

@@

Since the discover of Heisenberg's uncertainty principle~\cite{Heisenberg1983,544199,Jaeger2007},
non-commuting is one of the source of
